\chapter{Technical Preliminaries}
In this chapter we will introduce the Paxos consensus algorithm, Multiparty Session Types (\MPST), Fault-Tolerant Multiparty Session Types (\FTMPST), and some notation.
% FTMPST, Paxos, Some Notation
\input{technical_preliminaries/paxos.tex}

\section{Multiparty Session Types}
% TODO Introduce text from KP properly.
Multiparty Session Types (\MPST) are used to statically ensure correctly coordinated behavior in systems without global control (\cite{hondaYoshidaCarbone16,CoppoEtal15}).
One important such property is progress, \ie the absence of deadlock. Like with every other static typing approach, the main advantage is their efficiency, \ie they avoid the problem of state space explosion.

\MPST are designed to abstractly capture the structure of communication protocols.
They describe global behaviors as \emph{sessions}, \ie units of
conversations \cite{hondaYoshidaCarbone16,BettiniEtal08,BocciEtal10}. The participants of such sessions are called \emph{roles}.
\emph{Global types} specify protocols from a global point of view.
These types are used to reason about processes formulated
in a \emph{session calculus}. Most of the existing session calculi are
variants of the $ \pi $-calculus \cite{MilnerParrowWalker92}.

\input{technical_preliminaries/ftmpst.tex}

\section{Additional Notation}
In \cite{PetersEtal21} the authors introduced notation for the construction of global types and processes.

Let $ {\left( \bigodot_{1 \leq i \leq n} \pi_i \right)}.\GT $ abbreviate the sequence $ \pi_1.\ldots.\pi_n.\GT $ to simplify the presentation, where $ \GT \in \globalTypes $ is a global type and $ \pi_1, \ldots, \pi_n $ are sequences of prefixes. More precisely, each $ \pi_i $ is of the form $ \pi_{i, 1}.\ldots.\pi_{i, m} $ and each $ \pi_{i, j} $ is a type prefix of the form $ \GComUS{\Role_1}{\Role_2}{\Label}{\Sort} $ or $ \GBranW{\Role}{\Role[R]}{\Label_1.\LT_1 \oplus \ldots \oplus \Label_n.\LT_n \oplus \LabelD} $, where the latter case represents a \weakR branching prefix with the branches $ \Label_1, \ldots, \Label_n, \LabelD $, the default branch $ \LabelD $, and where the next global type provides the missing specification for the default case.

Let $ \left( \bigodot_{1 \leq i \leq n} \pi_i \right).\PT $ abbreviate the sequence $ \pi_1.\ldots.\pi_n.\PT $, where $ \PT \in \processes $ is a process and $ \pi_1, \ldots, \pi_n $ are sequences of prefixes.

% TODO Do we need this notation for local types?
% Let $\DotForall{1\leq i \leq n}{\pi_i}.\Type{}{}$ abbreviate the sequence $\pi_i.\ldots.\pi_n.\Type{}{}$, where $\Type{}{}\in\mathcal{T}$ is a local type and $\pi_1,\ldots,\pi_n$ are sequences of prefixes.
